Differentiable Optics with {\Large $\partial$}Lux: I - Deep Calibration of Flat Field and Phase Retrieval with Automatic Differentiation

### 2022-12-13 src/tex/ms.tex
[showyourwork] overleaf sync

The wavefront then encounters low-order phase errors parameterised by coefficients on Zernike polynomials. We include the first 4 radial terms, ignoring global piston, tip and tilt for a total of 7 terms. Coefficients were randomly drawn from a normal distribution of mean 0 and standard deviation 20\,nm, for a total of \variable{output/rms_opd_in.txt}\,nm RMS total \ac{opd}. These aberrations applied to the pupil mask and resulting \ac{psf} are shown in the middle panel of Figure~\ref{fig:optics}, where we see this induces a large amount of distortion in the \ac{psf}.

@@

This optimisation strategy performs well, with all of the parameters being recovered down to the noise level. This can be seen in Figure~\ref{fig:data_residual} with the right panel showing a sample residual of the data and model after optimisation, which is clearly only noise. Correlations and residual plots of the positions and fluxes after the optimisation are shown in Figure~\ref{fig:astro_params}. The 1-$sigma$ error bars indicate a poor recovery, however these are only marginalised over positions, fluxes and aberration, not the \ac{prf} which is the dominant noise source. These parameters are recovered to the expected distribution when performed without modelling the \ac{prf}. Figure~\ref{fig:aberrations} shows the recovery of the optical aberrations, with a final residual aberration of \variable{output/rms_opd_resid.txt} nm RMS. Finally, Figure~\ref{fig:flat_field} shows a correlation plot of the true and recovered sensitivity values and the corresponding residual histogram. The points of the correlation plot are colour-coded with the total counts for each pixel, showing as expected that pixels with higher photon counts having a better recovery of the PRF since these pixels have a greater \ac{snr}. Overall the parameters are very well recovered down to the noise level.

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.8\textwidth]{figs/ff.pdf}
    \caption{This figure shows the PRF values after optimisation. Left: Correlation between the pixel-level true and recovered values. Each point is color-coded with the total flux incident to each pixel, ie its \ac{snr}. The pixels with a greater signal are recovered better as expected. Right: Histogram of these residuals, with the majority of values being very well recovered and small symmetric about a residual of zero.}
    \label{fig:flat_field}
    % \script{gen_FF.py}
\end{figure*}

>>>>

The wavefront then encounters low-order phase errors parameterised by coefficients on Zernike polynomials. We include the first 4 radial terms, ignoring global piston, tip and tilt for a total of 7 terms. Coefficients were randomly drawn from a normal distribution of mean 0 and standard deviation 20\,nm, for a total of 
\textcolor{red}{showyourwork variable}
% \variable{output/rms_opd_in.txt}\,nm 
RMS total \ac{opd}. These aberrations applied to the pupil mask and resulting \ac{psf} are shown in the middle panel of Figure~\ref{fig:optics}, where we see this induces a large amount of distortion in the \ac{psf}.

@@

This optimisation strategy performs well, with all of the parameters being recovered down to the noise level. This can be seen in Figure~\ref{fig:data_residual} with the right panel showing a sample residual of the data and model after optimisation, which is clearly only noise. Correlations and residual plots of the positions and fluxes after the optimisation are shown in Figure~\ref{fig:astro_params}. The 1-$sigma$ error bars indicate a poor recovery, however these are only marginalised over positions, fluxes and aberration, not the \ac{prf} which is the dominant noise source. These parameters are recovered to the expected distribution when performed without modelling the \ac{prf}. Figure~\ref{fig:aberrations} shows the recovery of the optical aberrations, with a final residual aberration of 
\textcolor{red}{showyourwork variable}
% \variable{output/rms_opd_resid.txt} nm RMS. 
Finally, Figure~\ref{fig:flat_field} shows a correlation plot of the true and recovered sensitivity values and the corresponding residual histogram. The points of the correlation plot are colour-coded with the total counts for each pixel, showing as expected that pixels with higher photon counts having a better recovery of the PRF since these pixels have a greater \ac{snr}. Overall the parameters are very well recovered down to the noise level.

@@

\begin{figure*}
    \centering
    % \includegraphics[width=0.8\textwidth]{figs/ff.pdf}
    \includegraphics[width=0.8\textwidth]{figures/ff.pdf}
    \caption{This figure shows the PRF values after optimisation. Left: Correlation between the pixel-level true and recovered values. Each point is color-coded with the total flux incident to each pixel, ie its \ac{snr}. The pixels with a greater signal are recovered better as expected. Right: Histogram of these residuals, with the majority of values being very well recovered and small symmetric about a residual of zero.}
    \label{fig:flat_field}
    \script{plot_FF.py}
\end{figure*}
